\bf Hierarchical Forecasts Reconciliation

### 2019-04-11 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
Outlined first two papers

\usepackage{amssymb, qtree, bm, multirow, textcmds, siunitx,paralist}
\usepackage{mathrsfs, float, booktabs,todonotes,amsthm}
\usepackage[bb=boondox]{mathalfa}
\usepackage{tikz}
\usetikzlibrary{arrows,positioning,shapes,fit,calc}
\usepackage{amsfonts}

@@

	\if1\blind
	{
		\title{\bf Probabilistic Forecasts in Hierarchical~Time~Series}
		        \author{Puwasala Gamakumara\thanks{
		        The authors gratefully acknowledge the support of Australian Research Council Grant DP140103220.  We also thank Professor Mervyn Silvapulle for valuable comments.}\hspace{.2cm}\\
			    Department of Econometrics and Business Statistics,\\
			    Monash University,\\ VIC 3800, Australia.\\
			    Email: Puwasala.Gamakumara@monash.edu \\
			    and \\
			    Anastasios Panagiotelis\\
			    Department of Econometrics and Business Statistics,\\
		    	Monash University,\\ VIC 3800, Australia.\\
			    Email: Anastasios.Panagiotelis@monash.edu \\
			    and \\
		        George Athanasopoulos\\
		        Department of Econometrics and Business Statistics,\\
		        Monash University,\\ VIC 3800, Australia.\\
		        Email: george.athanasopoulos@monash.edu \\
		        and \\
	            Rob J Hyndman\\
	            Department of Econometrics and Business Statistics,\\
	            Monash University,\\ VIC 3800, Australia.\\
	            Email: rob.hyndman@monash.edu \\}
		\maketitle
	} \fi

	\if0\blind
	{
		\bigskip
		\bigskip
		\bigskip
		\begin{center}
			{\LARGE\bf Probabilistic Forecasts in Hierarchical~Time~Series}
		\end{center}
		\medskip
	} \fi

@@

\begin{abstract}
  Forecast reconciliation involves adjusting forecasts to ensure coherence with aggregation constraints. We extend this concept from point forecasts to probabilistic forecasts by redefining forecast reconciliation in terms of linear functions in general, and projections more specifically. New theorems establish that the true predictive distribution can be recovered in the elliptical case by linear reconciliation, and general conditions are derived for when this is a projection. A geometric interpretation is also used to prove two new theoretical results for point forecasting; that reconciliation via projection both preserves unbiasedness and dominates unreconciled forecasts in a mean squared error sense. Strategies for forecast evaluation based on scoring rules are discussed, and it is shown that the popular log score is an improper scoring rule with respect to the class of unreconciled forecasts when the true predictive distribution coheres with aggregation constraints. Finally, evidence from a simulation study shows that reconciliation based on an oblique projection, derived from the MinT method of \citet{Wickramasuriya2017} for point forecasting, outperforms both reconciled and unreconciled alternatives.
\end{abstract}

\noindent%
{\it Keywords:}  Forecast Reconciliation, Projections, Elliptical Distributions, Scoring Rules, High-dimensional Time Series.
\vfill

@@

Large collections of time series often follow some aggregation structure. For example, the electricity demand of a country can be disaggregated according to a geographic hierarchy of states, cities, and individual households. To ensure aligned decision making, it is important that forecasts at the most disaggregated level add up to forecasts at more aggregated levels. This property is called ``coherence''.  On the other hand ``reconciliation'' is a process whereby incoherent forecasts are made coherent. Both of these concepts have been developed extensively for point forecasting. Generalising both of these concepts, particularly the latter, to probabilistic forecasting is a gap that we seek to address in this work.  We do so by first providing a novel geometric interpretation to coherence and reconciliation in the point forecasting case. This can easily be generalised to probabilistic forecasting allowing us to derive further results for elliptical distributions as well as provide insight into forecast evaluation via multivariate  scoring rules.

Traditional approaches to ensure coherent point forecasts produce first-stage forecasts at a single level of the hierarchy. To describe these we use the small hierarchy in Figure~\ref{fig1} where the variable labelled $Tot$ is the sum of the series $A$ and series $B$, the series $A$ is the sum of series $AA$ and series $AB$ and the series $B$ is the sum of the series $BA$ and $BB$. In the bottom-up approach \citep{Dunn1976}, forecasts are produced at the most disaggregated level (series $AA$, $AB$, $BA$ and $BB$) and then summed to recover forecasts for all higher-level series. Alternatively, in the top-down approach \citep{Gross1990}, a top-level forecast is first produced (series $Tot$) and bottom-level forecasts are recovered by disaggregating the forecast using either historical or forecasted proportions. A middle-out approach is a hybrid between these two, that for the hierarchy in Figure~\ref{fig1} would produce first stage forecasts for series $A$ and $B$.

@@

In recent years, reconciliation methods introduced by \citet{Hyndman2011} have become increasingly popular. For these methods, first stage forecasts are independently produced for all series rather than series at a single level. Since these so-called `base' forecasts are rarely coherent in practice, they are subsequently adjusted or `reconciled' to ensure coherence.  Note that we use coherence and reconciliation as distinct terms, in contrast to their at times ambiguous usage in the past. To date, reconciliation has typically been formulated as a regression problem with alternative reconciliation methods resembling different least squares estimators. These include Ordinary Least Squares {OLS} \citep{Hyndman2011}, Weighted Least Squares {WLS} \citep{AthEtAl2017}, and a Generalised Least Squares (GLS) estimator \citep{Wickramasuriya2017} named MinT since it minimises the trace of the squared error matrix. These methods have been shown to outperform traditional alternatives across a range of simulated and real-world datasets \citep{AthEtAl2009,VanErven2015a,Wickramasuriya2017} since they use information at all levels of the hierarchy and, in some sense, hedge against the risk of model misspecification at a single level.

A shortcoming of the existing literature is a focus on point forecasting despite an increased understanding over the past decade of the importance of providing a full predictive distribution for forecast uncertainty \citep[see][and references therein]{Gneiting2014}. Indeed to the best of our knowledge, the (as yet unpublished) work of \citep{BenTaieb2017} is the only paper to deal with coherent probabilistic forecasts, and although they reconcile the means of the predictive distributions, the overall distributions are constructed in a bottom-up fashion rather than use a reconciliation process. In contrast, the main objective of our paper is to generalise both coherence and reconciliation from point to probabilistic forecasting.

To facilitate the extension of point forecast reconciliation to probabilistic forecasting, we first provide a geometric interpretation of existing point reconciliation methods, framing them in terms of projections. In addition to being highly intuitive, this allows us to establish a number of theoretical results. We prove two new theorems about point forecast reconciliation, the first showing that reconciliation via projections preserves the unbiasedness of base forecasts, while the second shows that reconciled forecasts dominate unreconciled forecasts via the distance reducing property of projections. We provide definitions of coherence and forecast reconciliation in the probabilistic setting, and describe how these definitions lead to a reconciliation procedure that merely involves a change of basis and marginalisation. We show that probabilistic reconciliation via linear transformations can recover the true predictive distribution as long as the latter is in the elliptical class. We provide conditions for which this linear transformation is a projection, and although this projection cannot be feasibly estimated in practice, we provide a heuristic argument in favour of MinT reconciliation.

We also cover the topic of forecast evaluation of probabilistic forecasts via scoring rules. In particular, we prove that for a coherent data generating process, the log score is not proper with respect to incoherent forecasts. Therefore we recommend the use of the energy score or variogram score for comparing reconciled to unreconciled forecasts. Two or more reconciled forecasts can be compared using log score, energy score or variogram score, although we show that comparisons should be made on the full hierarchy for the latter two scores.

The remainder of the paper is structured as follows. In Section~\ref{sec:definitions} coherence is defined geometrically for both point and probabilistic forecasts. Section~\ref{sec:reconciliation} contains definitions of point and probabilistic forecast reconciliation as well as our main theoretical results. In Section~\ref{sec:evaluation} we consider the evaluation of probabilistic hierarchical forecasts via scoring rules, while a simulation study comparing unreconciled probabilistic forecasts and different kinds of reconciled probabilistic forecasts is provided in Section~\ref{sec:gaussian}. Section~\ref{sec:conclusions} concludes with some discussion and thoughts on future research.

\section{Coherent forecasts}\label{sec:definitions}

@@

\subsection{Coherent probabilistic forecasts}\label{sec:cohprobf}

Let $(\mathbb{R}^m, \mathscr{F}_{\mathbb{R}^m}, \nu)$ be a probability triple, where $\mathscr{F}_{\mathbb{R}^m}$ is the usual Borel $\sigma$-algebra on $\mathbb{R}^m$. Let $\breve{\nu}$ be a probability measure on $\mathfrak{s}$ with $\sigma$-algebra $\mathscr{F}_{\mathfrak{s}}$. Here $\mathscr{F}_{\mathfrak{s}}$ is a collection of sets $s(\mathcal{B})$, where $s(\mathcal{B})$ denotes the image of the set $\mathcal{B}\in \mathscr{F}_{\mathbb{R}^m}$ under the mapping $s(.)$.

\begin{definition}[Coherent Probabilistic Forecasts]\label{def:cohprob}
  The measure $\breve{\nu}$ is coherent if it has the property
  \[
    \breve{\nu}(s(\mathcal{B})) = \nu(\mathcal{B}) \quad \forall \mathcal{B} \in \mathscr{F}_{\mathbb{R}^m},
  \]
\end{definition}

A probabilistic forecast for time $t+h$ is coherent if uncertainty in $\bm{\breve{y}}_{t+h}$ conditional on all information up to time $t$ is characterised by the probability triple $(\mathfrak{s},\mathscr{F}_{\mathfrak{s}},\breve{\nu})$.

These definitions of the coherent space $\mathfrak{s}$, coherent point and coherent probabilistic forecasts in terms of the mapping $s(.)$, may give the impression that the bottom-level series play an important role. However, alternative definitions could be formed using any set of basis vectors that span $\mathfrak{s}$. For example, consider the most simple three variable hierarchy where $y_{1,t}=y_{2,t}+y_{3,t}$. In this case the matrix $\bm{S}$ has columns $(1,1,0)'$ and $(1,0,1)'$ spanning $\mathfrak{s}$, and pre-multiplying by $\bm{S}$ transforms arbitrary values of $y_{2,t}$ and $y_{3,t}$ into a coherent vector for the full hierarchy. However the columns $(1,0,1)'$ and $(0,1,-1)'$ also span $\mathfrak{s}$ and define a mapping that transforms arbitrary values of $y_{1,t}$ and $y_{2,t}$ into a coherent vector for the full hierarchy. The definitions above could be made in terms of any series and not just the bottom-level series. In general, we call the series (or linear combinations thereof) used in the definitions of coherence \textit{basis series}. Unless stated otherwise, we will always assume that the basis series are the bottom-level series as in Definition~\ref{def:cohpoint} and Definition~\ref{def:cohprob}, since this facilitates comparison with existing approaches in the literature.

To the best of our knowledge, the only other definition of coherent probabilistic forecasts is given by \citet{BenTaieb2017} who define coherent probabilistic forecasts in terms of convolutions. According to their definition, probabilistic forecasts are coherent when a convolution of forecast distributions of disaggregate series is identical to the forecast distribution of the corresponding aggregate series. Their definition is consistent with our definition; our reason for providing a different definition is that the geometric understanding of coherence will facilitate our definitions of point and probabilistic forecast reconciliation to which we now turn our attention.

\section{Forecast reconciliation}\label{sec:reconciliation}

As discussed, reconciliation is distinct from coherence, since the former refers to a process whereby incoherent forecasts are made coherent. Although reconciliation methods for point forecasts are extant in the literature they are rarely defined explicitly.  We do so here in slightly more general terms than usual. We then extend this idea to the novel concept of probabilistic reconciliation.

\subsection{Point forecast reconciliation}

@@

Point reconciliation methods based on projections will always minimise the distance between unreconciled and reconciled forecasts, however the specific distance will depend on the choice of $\bm{R}$. For example OLS minimises the Euclidean distance between $\hat{\bm{y}}_{t+h|t}$ and $\tilde{\bm{y}}_{t+h|t}$, while \citet{Wickramasuriya2017} show that MinT minimises the Mahalonobis distance between $\hat{\bm{y}}_{t+h|t}$ and $\tilde{\bm{y}}_{t+h|t}$. Bottom-up methods minimise distance between reconciled and unreconciled forecasts only along dimensions corresponding to the bottom-level series. Therefore bottom-up methods should be thought of as a boundary case of reconciliation methods, since they ultimately do not use information at all levels of the hierarchy.

Before generalising the concept of point reconciliation to probabilistic forecasts, we state two theorems that motivate the use of projections for point forecast reconciliation. First, let $\bm{\mu}_{t+h|t}:=\E(\bm{y}_{t+h}\mid\bm{y}_{1},\dots,\bm{y}_{t})$ and assume $\hat{\bm{y}}_{t+h|t}$ is an unbiased prediction; that is $\E_{1:t}(\hat{\bm{y}}_{t+h|t})=\mu_{t+h|t}$, where the subscript $1:t$ denotes an expectation taken over the training sample.

@@

\subsection{Probabilistic forecast reconciliation}

We now extend the methodology of point forecast reconciliation to probabilistic forecasts.
%For probabilistic forecasts, reconciliation implies finding the probability measure of the coherent forecasts using the information from an incoherent probabilistic forecast measure. A more formal definition is given below.
Let $(\mathbb{R}^n, \mathscr{F}_{\mathbb{R}^n}, \hat{\nu})$ be a probability triple that is not coherent and which characterises forecast uncertainty for all variables in the hierarchy at time $t+h$ conditional on all information up to time $t$. This is obtained from the first stage of the forecasting process; e.g., by modelling and forecasting each series individually. Let $g:\mathbb{R}^n \rightarrow \mathbb{R}^m $ be a linear function, and let $(\mathbb{R}^m, \mathscr{F}_{\mathbb{R}^m}, \nu)$ be a probability triple defined on $\mathbb{R}^m$.

\begin{definition} \label{def:reconprob}
  The reconciled probability measure of $\hat{\nu}$ with respect to the mapping $g(.)$ is a probability measure $\tilde{\nu}$ on $\mathfrak{s}$ with $\sigma$-algebra $\mathscr{F}_\mathfrak{s}$ such that
  \begin{equation}
  \tilde{\nu}(s(\mathcal{B})) = \nu(\mathcal{B})= \hat{\nu}(g^{-1}(\mathcal{B})) \qquad \forall \mathcal{B} \in \mathscr{F}_{\mathbb{R}^m}\,,
  \end{equation}
  where $g^{-1}(\mathcal{B}):=\{\breve{\bm{y}}\in \mathbb{R}^n:g(\breve{\bm{y}})\in \mathcal{B}\}$ is the pre-image of $\mathcal{B}$, that is the set of all points in $\mathbb{R}^n$ that $g(.)$ maps to a point in $\mathcal{B}$.
\end{definition}

This definition extends the notion of forecast reconciliation to the probabilistic setting. Under point reconciliation methods, the reconciled point forecast is equal to the unreconciled point forecast after the latter is passed through two linear functions. Similarly, probabilistic forecast reconciliation assigns the same probability to two sets where the points in one set are obtained by passing all points in the other set through two linear functions. This is depicted in Figure~\ref{fig:probfr_sch} schematically when $s\circ g$ is a projection.

\begin{figure}
	\input{Figs/probforerec_schematic.tex}
	\caption{Summary of probabilistic forecast reconciliation. The probability that $\bm{y}_{t+h}$ lies in the red line segment under the reconciled probabilistic forecast is defined to be equal to the probability that $\bm{y}_{t+h}$ lies in the shaded blue area under the unreconciled probabilistic forecast. Note that since the smallest hierarchy involves three dimensions, this figure is only a schematic.}\label{fig:probfr_sch}
\end{figure}

Recall that when $s\circ g$ is a projection, the case of point forecast reconciliation can be broken down into three steps.
\begin{compactenum}
\item  $\hat{\bm{y}}_{t+h|t}$ is transformed into coordinates $\tilde{\bm{b}}_{t+h|t}$ and $\tilde{\bm{a}}_{t+h|t}$ via a change of basis.
\item $\tilde{\bm{a}}_{t+h|t}$ is discarded and $\tilde{\bm{b}}_{t+h|t}$ are kept as the bottom-level reconciled forecasts.
\item Reconciled forecasts for the entire hierarchy are recovered via $\tilde{\bm{y}}_{t+h|t}=\bm{S}\tilde{\bm{b}}_{t+h|t}$.
\end{compactenum}
We now outline the analogous steps for probabilistic forecasts when predictive densities are available.

While $\hat{\nu}$ is a probability measure for an $n$-vector $\hat{\bm{y}}_{t+h|t}$, probability statements in terms of a different coordinate system can be made via an appropriate change of basis. Letting $f(.)$ be generic notation for a probability density function, and following the notation from our definition of point forecast reconciliation where $\hat{\bm{y}}_{t+h|t}=\bm{S}\tilde{\bm{b}}_{t+h|t}+\bm{R}\tilde{\bm{a}}_{t+h|t}$, we obtain
\begin{equation}
f(\hat{\bm{y}}_{t+h|t})=f(\bm{S}\tilde{\bm{b}}_{t+h|t}+\bm{R}\tilde{\bm{a}}_{t+h|t})|(\bm{S}~\bm{R})|
\end{equation}
The expression $\hat{\nu}(g^{-1}(\mathcal{B}))$ in Definition~\ref{def:reconprob} is equivalent to the probability statement $\text{Pr}(\hat{\bm{y}}_{t+h|t}\in g^{-1}(\mathcal{B}))$. After the change of basis, this is equivalent to $\text{Pr}(\tilde{\bm{b}}\in \mathcal{B})$, which implies
\begin{align}
\text{Pr}(\hat{\bm{y}}_{t+h|t}\in g^{-1}(\mathcal{B}))&=\int\limits_{g^{-1}(\mathcal{B})}f(\hat{\bm{y}}_{t+h|t})d\hat{\bm{y}}_{t+h|t}\\
&=\int\limits_{\mathcal{B}}\int f(\bm{S}\tilde{\bm{b}}_{t+h|t}+\bm{R}\tilde{\bm{a}}_{t+h|t})|(\bm{S}~\bm{R})|d\tilde{\bm{a}}_{t+h|t}d\tilde{\bm{b}}_{t+h|t}.
\end{align}
After integrating out over $\tilde{\bm{a}}_{t+h|t}$, a step analogous to setting $\tilde{\bm{a}}_{t+h|t}=0$ for point forecasting, we obtain an expression that gives the probability that the reconciled bottom-level series lies in the region $\mathcal{B}$. This corresponds to $\nu(\mathcal{B})$ in Definition~\ref{def:reconprob}. To make a valid probability statement about the entire hierarchy we simply use the bottom-level probabilistic forecasts together with Definition~\ref{def:cohprob}.

\subsubsection*{Example: Gaussian Distributions}

Suppose an unreconciled probabilistic forecast is Gaussian with mean $\hat{\bm{\mu}}$ and variance-covariance matrix $\hat{\bm{\Sigma}}$. The subscripts $t+h|t$ are suppressed for brevity. Let the unreconciled density be given by
\begin{equation}
  f(\hat{\bm{y}})=(2\pi)^{-n/2}|\hat{\bm{\Sigma}}|^{-1/2}\exp\left\{-\frac{1}{2}\left[(\hat{\bm{y}}-\hat{\bm{\mu}})'\hat{\bm{\Sigma}}^{-1}(\hat{\bm{y}}-\hat{\bm{\mu}})\right]\right\}.
\end{equation}
In an alternative basis,
\begin{equation}
f(\tilde{\bm{b}},\tilde{\bm{a}})=(2\pi)^{-\frac{n}{2}}\Big|\hat{\bm{\Sigma}}\Big|^{-\frac{1}{2}}\Big|(\bm{S} ~  \bm{R})\Big|\exp\{-\frac{1}{2}q\}\,,
\end{equation}
where
\begin{equation}
q=(\bm{S}\tilde{\bm{b}}+\bm{R}\tilde{\bm{a}}-\hat{\bm{\mu}})' \hat{\bm{\Sigma}}^{-1}(\bm{S}\tilde{\bm{b}}+\bm{R}\tilde{\bm{a}}-\hat{\bm{\mu}}).
\end{equation}
The quadratic form $q$ can be rearranged as
\begin{align*}
q& =
\left((\bm{S} ~  \bm{R})\bt-\hat{\bm{\mu}}\right)' \hat{\bm{\Sigma}}^{-1}\left((\bm{S} ~ \bm{R})\bt-\hat{\bm{\mu}}\right),\\
& =
\left(\bt-(\bm{S} ~ \bm{R})^{-1}\hat{\bm{\mu}}_{t+h}\right)' \Big[(\bm{S}  \bm{R})^{-1}\hat{\bm{\Sigma}_{t+h}}\left((\bm{S} ~ \bm{R})^{-1}\right)'\Big]^{-1}
\left(\bt-(\bm{S} ~ \bm{R})^{-1}\hat{\bm{\mu}}_{t+h}\right)\,.
\end{align*}
Recall that
\[
  (\bm{S} ~ \bm{R})^{-1} =
  \begin{pmatrix}(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot  \\ (\bm{S}'_\bot \bm{R})^{-1}\bm{S}'_\bot \end{pmatrix} :=
  \begin{pmatrix}
  \bm{G} \\\bm{H}
  \end{pmatrix}\,.
\]
Then $q$ can be rearranged further as
\begin{align*}
q& =%\frac{1}{(2\pi)^{\frac{n}{2}}\Big|\hat{\bm{\Sigma}}_{t+h}\Big|^{\frac{1}{2}}\Big|\PQ \Big|}
%\exp \Big\{-\frac{1}{2}
\left[\bt-\PQ\hat{\bm{\mu}}_{t+h}\right]'%\\[-0.5cm]
\left[\PQ\hat{\bm{\Sigma}_{t+h}}\PQ'\right]^{-1}\left[\bt-\PQ\hat{\bm{\mu}}_{t+h}\right] %\Big\},
\\[0.5cm]
 & =%\frac{1}{(2\pi)^{\frac{n}{2}}\Big|\PQ\hat{\bm{\Sigma}_{t+h}}\PQ'\Big|^{\frac{1}{2}}}
%\exp \Big\{-\frac{1}{2}
\begin{pmatrix}\tilde{\bm{b}} - \bm{G}\hat{\bm{\mu}}\\ \tilde{\bm{a}}- \bm{H}\hat{\bm{\mu}}\end{pmatrix}' %&\\[-0.5cm]
%& \hspace*{7cm}
 \left[\PQ\hat{\bm{\Sigma}_{t+h}}\PQ'\right]^{-1}\begin{pmatrix}\tilde{\bm{b}} - \bm{G}\hat{\bm{\mu}}\\ \tilde{\bm{a}}- \bm{H}\hat{\bm{\mu}}\end{pmatrix}. %\Big\}.
\end{align*}
%Since $\Big[\PQ\hat{\bm{\Sigma}_{t+h}}\PQ'\Big] = \begin{pmatrix}
%\bm{P}\hat{\bm{\Sigma}_{t+h}}\bm{P}' & \bm{P}\hat{\bm{\Sigma}_{t+h}}\bm{Q}'
%\bm{Q}\hat{\bm{\Sigma}_{t+h}}\bm{P}' & \bm{Q}\hat{\bm{\Sigma}_{t+h}}\bm{Q}'
%\end{pmatrix}$ we have

>>>>

\usepackage{amssymb, qtree, bm, multirow, textcmds, siunitx,paralist}
\usepackage{mathrsfs, float, booktabs,todonotes,amsthm, xcolor}
\usepackage[bb=boondox]{mathalfa}
\usepackage{tikz}
\usetikzlibrary{arrows,positioning,shapes,fit,calc}
\usepackage{amsfonts}

@@

	\if1\blind
	{
		\title{\bf Hierarchical Forecasts Reconciliation}
		\author{Puwasala Gamakumara\thanks{
				The authors gratefully acknowledge the support of Australian Research Council Grant DP140103220.  We also thank Professor Mervyn Silvapulle for valuable comments.}\hspace{.2cm}\\
			Department of Econometrics and Business Statistics,\\
			Monash University,\\ VIC 3800, Australia.\\
			Email: Puwasala.Gamakumara@monash.edu \\
			and \\
			Anastasios Panagiotelis\\
			Department of Econometrics and Business Statistics,\\
			Monash University,\\ VIC 3800, Australia.\\
			Email: Anastasios.Panagiotelis@monash.edu \\
			and \\
			George Athanasopoulos\\
			Department of Econometrics and Business Statistics,\\
			Monash University,\\ VIC 3800, Australia.\\
			Email: george.athanasopoulos@monash.edu \\
			and \\
			Rob J Hyndman\\
			Department of Econometrics and Business Statistics,\\
			Monash University,\\ VIC 3800, Australia.\\
			Email: rob.hyndman@monash.edu \\}
		\maketitle
	} \fi

	\if0\blind
	{
		\bigskip
		\bigskip
		\bigskip
		\begin{center}
			{\LARGE\bf Hierarchical Forecasts Reconciliation}
		\end{center}
		\medskip
	} \fi

@@

	\begin{abstract} TBC
		%  Forecast reconciliation involves adjusting forecasts to ensure coherence with aggregation constraints. We extend this concept from point forecasts to probabilistic forecasts by redefining forecast reconciliation in terms of linear functions in general, and projections more specifically. New theorems establish that the true predictive distribution can be recovered in the elliptical case by linear reconciliation, and general conditions are derived for when this is a projection. A geometric interpretation is also used to prove two new theoretical results for point forecasting; that reconciliation via projection both preserves unbiasedness and dominates unreconciled forecasts in a mean squared error sense. Strategies for forecast evaluation based on scoring rules are discussed, and it is shown that the popular log score is an improper scoring rule with respect to the class of unreconciled forecasts when the true predictive distribution coheres with aggregation constraints. Finally, evidence from a simulation study shows that reconciliation based on an oblique projection, derived from the MinT method of \citet{Wickramasuriya2017} for point forecasting, outperforms both reconciled and unreconciled alternatives.
	\end{abstract}

%	\noindent%
%	{\it Keywords:}  Forecast Reconciliation, Projections, Elliptical Distributions, Scoring Rules, High-dimensional Time Series.
%	\vfill

@@

%	Large collections of time series often follow some aggregation structure. For example, the electricity demand of a country can be disaggregated according to a geographic hierarchy of states, cities, and individual households. To ensure aligned decision making, it is important that forecasts at the most disaggregated level add up to forecasts at more aggregated levels. This property is called ``coherence''.  On the other hand ``reconciliation'' is a process whereby incoherent forecasts are made coherent. Both of these concepts have been developed extensively for point forecasting. Generalising both of these concepts, particularly the latter, to probabilistic forecasting is a gap that we seek to address in this work.  We do so by first providing a novel geometric interpretation to coherence and reconciliation in the point forecasting case. This can easily be generalised to probabilistic forecasting allowing us to derive further results for elliptical distributions as well as provide insight into forecast evaluation via multivariate  scoring rules. 
%	
%	Traditional approaches to ensure coherent point forecasts produce first-stage forecasts at a single level of the hierarchy. To describe these we use the small hierarchy in Figure~\ref{fig1} where the variable labelled $Tot$ is the sum of the series $A$ and series $B$, the series $A$ is the sum of series $AA$ and series $AB$ and the series $B$ is the sum of the series $BA$ and $BB$. In the bottom-up approach \citep{Dunn1976}, forecasts are produced at the most disaggregated level (series $AA$, $AB$, $BA$ and $BB$) and then summed to recover forecasts for all higher-level series. Alternatively, in the top-down approach \citep{Gross1990}, a top-level forecast is first produced (series $Tot$) and bottom-level forecasts are recovered by disaggregating the forecast using either historical or forecasted proportions. A middle-out approach is a hybrid between these two, that for the hierarchy in Figure~\ref{fig1} would produce first stage forecasts for series $A$ and $B$.
%	
%	
%	In recent years, reconciliation methods introduced by \citet{Hyndman2011} have become increasingly popular. For these methods, first stage forecasts are independently produced for all series rather than series at a single level. Since these so-called `base' forecasts are rarely coherent in practice, they are subsequently adjusted or `reconciled' to ensure coherence.  Note that we use coherence and reconciliation as distinct terms, in contrast to their at times ambiguous usage in the past. To date, reconciliation has typically been formulated as a regression problem with alternative reconciliation methods resembling different least squares estimators. These include Ordinary Least Squares {OLS} \citep{Hyndman2011}, Weighted Least Squares {WLS} \citep{AthEtAl2017}, and a Generalised Least Squares (GLS) estimator \citep{Wickramasuriya2017} named MinT since it minimises the trace of the squared error matrix. These methods have been shown to outperform traditional alternatives across a range of simulated and real-world datasets \citep{AthEtAl2009,VanErven2015a,Wickramasuriya2017} since they use information at all levels of the hierarchy and, in some sense, hedge against the risk of model misspecification at a single level.
%	
%	A shortcoming of the existing literature is a focus on point forecasting despite an increased understanding over the past decade of the importance of providing a full predictive distribution for forecast uncertainty \citep[see][and references therein]{Gneiting2014}. Indeed to the best of our knowledge, the (as yet unpublished) work of \citep{BenTaieb2017} is the only paper to deal with coherent probabilistic forecasts, and although they reconcile the means of the predictive distributions, the overall distributions are constructed in a bottom-up fashion rather than use a reconciliation process. In contrast, the main objective of our paper is to generalise both coherence and reconciliation from point to probabilistic forecasting.
%	
%	To facilitate the extension of point forecast reconciliation to probabilistic forecasting, we first provide a geometric interpretation of existing point reconciliation methods, framing them in terms of projections. In addition to being highly intuitive, this allows us to establish a number of theoretical results. We prove two new theorems about point forecast reconciliation, the first showing that reconciliation via projections preserves the unbiasedness of base forecasts, while the second shows that reconciled forecasts dominate unreconciled forecasts via the distance reducing property of projections. We provide definitions of coherence and forecast reconciliation in the probabilistic setting, and describe how these definitions lead to a reconciliation procedure that merely involves a change of basis and marginalisation. We show that probabilistic reconciliation via linear transformations can recover the true predictive distribution as long as the latter is in the elliptical class. We provide conditions for which this linear transformation is a projection, and although this projection cannot be feasibly estimated in practice, we provide a heuristic argument in favour of MinT reconciliation.
%	
%	We also cover the topic of forecast evaluation of probabilistic forecasts via scoring rules. In particular, we prove that for a coherent data generating process, the log score is not proper with respect to incoherent forecasts. Therefore we recommend the use of the energy score or variogram score for comparing reconciled to unreconciled forecasts. Two or more reconciled forecasts can be compared using log score, energy score or variogram score, although we show that comparisons should be made on the full hierarchy for the latter two scores.
%	
%	The remainder of the paper is structured as follows. In Section~\ref{sec:definitions} coherence is defined geometrically for both point and probabilistic forecasts. Section~\ref{sec:reconciliation} contains definitions of point and probabilistic forecast reconciliation as well as our main theoretical results. In Section~\ref{sec:evaluation} we consider the evaluation of probabilistic hierarchical forecasts via scoring rules, while a simulation study comparing unreconciled probabilistic forecasts and different kinds of reconciled probabilistic forecasts is provided in Section~\ref{sec:gaussian}. Section~\ref{sec:conclusions} concludes with some discussion and thoughts on future research.

	\section{Forecasts reconciliation}\label{sec:definitions}

@@

@@

	These definitions of the coherent space $\mathfrak{s}$, coherent point and coherent probabilistic forecasts in terms of the mapping $s(.)$, may give the impression that the bottom-level series play an important role. However, alternative definitions could be formed using any set of basis vectors that span $\mathfrak{s}$. For example, consider the most simple three variable hierarchy where $y_{1,t}=y_{2,t}+y_{3,t}$. In this case the matrix $\bm{S}$ has columns $(1,1,0)'$ and $(1,0,1)'$ spanning $\mathfrak{s}$, and pre-multiplying by $\bm{S}$ transforms arbitrary values of $y_{2,t}$ and $y_{3,t}$ into a coherent vector for the full hierarchy. However the columns $(1,0,1)'$ and $(0,1,-1)'$ also span $\mathfrak{s}$ and define a mapping that transforms arbitrary values of $y_{1,t}$ and $y_{2,t}$ into a coherent vector for the full hierarchy. The definitions above could be made in terms of any series and not just the bottom-level series. In general, we call the series (or linear combinations thereof) used in the definitions of coherence \textit{basis series}. Unless stated otherwise, we will always assume that the basis series are the bottom-level series as in Definition~\ref{def:cohpoint}, since this facilitates comparison with existing approaches in the literature.

	\subsection{Point forecast reconciliation}\label{sec:reconciliation}

	As discussed, reconciliation is distinct from coherence, since the former refers to a process whereby incoherent forecasts are made coherent. Although reconciliation methods for point forecasts are extant in the literature they are rarely defined explicitly.  We do so here in slightly more general terms than usual. 
	%We then extend this idea to the novel concept of probabilistic reconciliation.

@@

	Point reconciliation methods based on projections will always minimise the distance between unreconciled and reconciled forecasts, however the specific distance will depend on the choice of $\bm{R}$. For example OLS minimises the Euclidean distance between $\hat{\bm{y}}_{t+h|t}$ and $\tilde{\bm{y}}_{t+h|t}$, while \citet{Wickramasuriya2017} show that MinT minimises the Mahalonobis distance between $\hat{\bm{y}}_{t+h|t}$ and $\tilde{\bm{y}}_{t+h|t}$. \textcolor{red}{Explain why MinT works well}. Bottom-up methods minimise distance between reconciled and unreconciled forecasts only along dimensions corresponding to the bottom-level series. Therefore bottom-up methods should be thought of as a boundary case of reconciliation methods, since they ultimately do not use information at all levels of the hierarchy.

	We now state two theorems that motivate the use of projections for point forecast reconciliation. First, let $\bm{\mu}_{t+h|t}:=\E(\bm{y}_{t+h}\mid\bm{y}_{1},\dots,\bm{y}_{t})$ and assume $\hat{\bm{y}}_{t+h|t}$ is an unbiased prediction; that is $\E_{1:t}(\hat{\bm{y}}_{t+h|t})=\mu_{t+h|t}$, where the subscript $1:t$ denotes an expectation taken over the training sample.

@@

	\section{Bias correction}

	\section{Application}

	\section{Conclusions}
